---
title: "Rmarkdown Presentation and plotly"
author: "Olagunju Ayodeji"
date: "April 9, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Creating a webpage that involves plotly
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 
## Slide with R Output
My dataset is airport dataset, containing all the parameters below.
```{r, echo = FALSE}
library(plotly)
library(ggplot2)
Airport <- read.csv("C:/Users/djolas/Downloads/airports.csv")
head(Airport)
```

## Created 10 April, 2019.

```{r cars, echo=FALSE, message=FALSE}
plot_ly(Airport, x = ~LATITUDE, y = ~LONGITUDE, type = "scatter", mode ="lines+markers", color = ~factor(STATE))
```

